Data- and Systems Paper: your title here

### 2016-04-06 milestone1/paper/paper.tex
moved StyleFiles to root
report progress

\documentclass[runningheads,a4paper]{StyleFiles/llncs}

@@

\section{Introduction}
% Introduce the sections that follow. What is the core contribution of this paper, and why is that interesting? It is useful to start with a real-life problem, and then explain how your system/dataset (will) solve(s) that problem by means of KR technology. Why is this novel? Has this (or something similar) been done before?

@@

\section{Data sources}
% which datasets have you used and converted? Provide the core properties of those datasets. Also describe other datasets that you might want to integrate, and even data that still needs to be found, or even created.

>>>>

\documentclass[runningheads,a4paper]{../../StyleFiles/llncs}

@@

\section{Introduction}
% Introduce the sections that follow. What is the core contribution of this paper, and why is that interesting? It is useful to start with a real-life problem, and then explain how your system/dataset (will) solve(s) that problem by means of KR technology. Why is this novel? Has this (or something similar) been done before?
%TODO read WHOLE section again and make it pretty
Amsterdam is a busy city that offers a variety of events and a common problem when attending such events is that Parking Spots are often scarce. Specifically, for handicap people this is an issue that should not be overlooked since they require more time to commute. Hence, having knowledge about close parking spots is specially useful to them.

However, acquiring this information is not straightforward. The location of venues is not associated with Parking Spot locations, and users usually have to find them themselves by means of maps or driving around. Solving this problem would bring benefits to attendees. %TODO is this novel?

In this project we create a web application that serves as a unique point for finding locations of venues and parking spots related to an event. We decided to work with Museum Galleries and Theaters to keep the scope of the project manageable. To do so we convert existing datasets to RDF format and query them to get the desired results.

In the following section we delve deeper into cases where our proposed solution could be applied. Next, we describe the datasets and continue to explain the data management process to abstract the knowledge from those datasets. Then, we explain the semantics in our data set and provide examples of the queries we used to build the application. We finalize with a demo of the application and a discussion of the work done.

@@

As stated in the introduction, the integration of venues and parking spot locations may bring benefits to attendees. Our application will provide a convenient and time-saving option for attendees to find parking spots. Furthermore, by using our application it is guaranteed that the best parking spot will be suggested %TODO not sure about this though ...

Hereby we provide three concrete use-cases where our application's benefits are to be maximized.

\begin{enumerate}
	% Planning in advance
	\item John is in a wheelchair and wants to go to an exhibition in Van Gogh Museum Friday night. John likes to plan things in advance and would like to know where the parking slots closest to the theater are. \\
	The day before the show, John uses our application to find such parking spots and heads to the show confidently. 
	% Quick search once in the theater (on the fly)
	\item Peter is rushing to get to an exhibition in Van Gogh Museum and is looking for the closest parking spots. He quickly browses our application and finds an area with several parking spots. He drives in that direction hoping to find an available spot. 
	% Event manager
	\item Mary is an event organizer who wants to host an exhibition in a Museum next month. She is looking for an accessible venue so she would like to see the distribution of parking spots around the main galleries in Amsterdam. She uses the interactive visualization in our application to explore and choose the best venue.
\end{enumerate}

\section{Data sources}
% which datasets have you used and converted? Provide the core properties of those datasets. Also describe other datasets that you might want to integrate, and even data that still needs to be found, or even created.
We decided to integrate the Gemeente's open data about theater events, museums
and galleries and handicap's parking slots. Those datasets are available in CSV
or JSON formats. We chose to convert from the JSON format because it is a more
powerful representation than CSV and because JSON and RDF formats can be easily
mapped one to another.

\subsection{Theaters Dataset}
% TODO describe theaters dataset (fields, contained data, semantics)

\subsection{Museums and Galleries Dataset}
% TODO describe museums and galleries dataset

\subsection{Handicap's Parking Slots Dataset}
% TODO describe this dataset
